Current and future constraints on primordial magnetic fields

### 2017-04-24 pmf.tex
i

We thank the \changed{referee as well as} Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
C. Reichardt is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 
CF acknowledges support from NASA grants NASA NNX16AJ69G and NASA NNX16AF39G. 
This research used resources of the National Energy Research Scientific Computing Center, which is supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231. 
We acknowledge the use of the Legacy Archive for Microwave Background Data Analysis (LAMBDA). Support for LAMBDA is provided by the NASA Office of Space Science.

>>>>

We thank the \changed{referee as well as} Srinivasan Raghunathan and Federico Bianchini for valuable feedback on the manuscript. 
CR is the recipient of an Australian Research Council Future Fellowship (FT150100074), and also acknowledges support from the University of Melbourne. 
CF acknowledges support from NASA grants NASA NNX16AJ69G and NASA NNX16AF39G. 
This research used resources of the National Energy Research Scientific Computing Center, which is supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231. 
We acknowledge the use of the Legacy Archive for Microwave Background Data Analysis (LAMBDA). Support for LAMBDA is provided by the NASA Office of Space Science.
